### 2017-11-28 paper/sections/1_introduction.tex
paper: fix typos
Signed-off-by: Michael Sevilla <mikesevilla3@gmail.com>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But the policies for what data to evict and when to
evict are specific to the application's behavior and the system's configuration
(hardware, settings, etc.) so a new workload may prove to be a poor match for
the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. In this paper, we evaluate a
variety of caching policies using our data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can be adapted to different workloads.

@@

% What is Mantle
In this paper we are presenting the successful use of the Mantle policy language and engine to manage the dynamically-sized cache. Mantle provides a control plane that
injects policies into a running storage system, such as a file system or key-value store. While Mantle
was originally designed for file system metadata load balancing~\cite{sevilla:sc15-mantle},
we found that it works surprisingly well for specifying cache management policies without requiring users to possess extensive knowledge about the internals of storage systems. We show that our framework:

>>>>

Storage systems use software-based caches to improve performance but the
policies that guide what data to evict and when to evict vary with the use
case. For example, caching file system metadata on clients and servers reduces
the number of remote procedure calls and improves the performance of
create-heavy workloads common in HPC~\cite{ren:sc2014-indexfs,
patil:fast2011-giga+}. But the policies for what data to evict and when to
evict are specific to the application's behavior and the system's configuration
(hardware, settings, etc.) so a new workload may prove to be a poor match for
the selected caching
policy~\cite{xiao:socc15-shardfs,brandt:msst2003-lh,sevilla:sc15-mantle,
weil:sc2004-dyn-metadata, weil:osdi2006-ceph}. We evaluate a
variety of caching policies using our data management language/policy engine and
arrive at a customized policy that works well for our target application.  This
process of trying general policies and quickly iterating to a customized
solution shows that our prototype can be adapted to different workloads.

@@

% What is Mantle

In this paper we are presenting the successful use of our data management
language and Mantle policy engine to control the behavior of ParSplice's
caches. Mantle provides a control plane that injects policies into a running
storage system, such as a file system or key-value store. While Mantle was
originally designed for file system metadata load
balancing~\cite{sevilla:sc15-mantle}, we find that it works surprisingly well
for specifying cache management policies without requiring users to possess
extensive knowledge about the internals of storage systems. We show that our
framework:
